\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Ginger Biscuits with Peaches}{8-10 servings}{30 minutes prep, 18 minutes baking}

\Ingredient{6 peaches}
\Ingredient{1 tablespoon maple sugar (or cane sugar)}
Slice peaches into wedges and sprinkle sugar over them. Refrigerate.
Start preheating the oven to 400\0F.

\Ingredient{1 tablespoon maple sugar (or cane sugar)}
\Ingredient{1 cup \wwp}
\Ingredient{1 cup \ap}
\Ingredient{\fr12 teaspoon sea salt}
\Ingredient{2 teaspoons baking powder}
\Ingredient{\fr12 teaspoon baking soda}
Combine in a stand mixer.

\Ingredient{1 stick cold butter, in tablespoon-sized pieces}
Add gradually and mix until butter is broken into pea-size pieces.

\Ingredient{\fr12 cup crystallized ginger, finely diced}
Add and stir in.

\Ingredient{1 large egg}
\Ingredient{\fr12 teaspoon vanilla extract}
\Ingredient{\fr12 cup buttermilk (plus 1-2 teaspoons)}
Beat together. Add to dry ingredients and stir in with a fork. If the mixture is too dry, add extra 1-2 teaspoons of buttermilk. The dough should be shaggy and barely moist.
Turn dough onto a counter that is lightly floured. Knead lightly, then roll or pat dough into a circle about \fr34 inch thick. Cut out 2-inch circles and place close together on a baking sheet. Bake until golden, about 12-18 minutes.

\Ingredient{\fr12 pint cold whipping cream}
\Ingredient{1 tablespoon sugar}
\Ingredient{\fr18 teaspoon almond extract}
Whip the cream to serve on top of the biscuits, with the peaches.

\end{recipe}

\end{document}
