\documentclass[../Cookbook.tex]{subfiles}

\begin{document}
% http://www.seriouseats.com/recipes/2016/12/print/the-best-roast-potatoes-ever-recipe.html
\begin{recipe}{Roast Potatoes}{4 servings}{30 minutes prep, 45 minutes cooking}

\begin{itemize}
	\item Large chunks of potato maximize the contrast between exterior and interior.
	\item Parboiling the potatoes in alkaline water breaks down their surfaces, creating tons of starchy slurry for added surface area and crunch.
	\item Infusing the oil with garlic and herbs gives the potato crust extra flavor.
\end{itemize}

Adjust oven rack to center position and preheat oven to 230\0C (or 200\0C if using convection).

\Ingredient{2 liters water}
\Ingredient{25 grams salt}
\Ingredient{4 grams baking soda}
\Ingredient{2 kilograms Russet or Yukon Gold potatoes}
Heat water in a large pot over high heat until boiling. Add salt, baking soda, and potatoes and stir. Return to a boil, reduce to a simmer, and cook until a knife meets little resistance when inserted into a potato chunk, about 10 minutes after returning to a boil.

\Ingredient{75 milliliters olive oil, duck fat, or beef fat}
\Ingredient{5 milliliters fresh rosemary leaves, chopped}
\Ingredient{1 milliliter freshly ground black pepper}
\Ingredient{5 milliliters fresh parsley leaves, minced}
\Ingredient{5 medium cloves garlic}
Meanwhile, combine olive oil, duck fat, or beef fat with rosemary, garlic, and a few grinds of black pepper in a small saucepan and heat over medium heat. Cook, stirring and shaking pan constantly, until garlic just begins to turn golden, about 3 minutes. Immediately strain oil through a fine-mesh strainer set in a large bowl. Set garlic/rosemary mixture aside and reserve separately.

\newstep
When potatoes are cooked, drain carefully and let them rest in the pot for about 30 seconds to allow excess moisture to evaporate. Transfer to bowl with infused oil, season to taste with a little more salt and pepper, and toss to coat, shaking bowl roughly, until a thick layer of mashed potato–like paste has built up on the potato chunks.

\newstep
Transfer potatoes to a large rimmed baking sheet and separate them, spreading them out evenly. Transfer to oven and roast, without moving, for 20 minutes. Using a thin, flexible metal spatula to release any stuck potatoes, shake pan and turn potatoes. Continue roasting until potatoes are deep brown and crisp all over, turning and shaking them a few times during cooking, 30 to 40 minutes longer.

\newstep
Transfer potatoes to a large bowl and add garlic/rosemary mixture and minced parsley. Toss to coat and season with more salt and pepper to taste. Serve immediately.

\end{recipe}

\end{document}
