\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Salami Three Cheese Stromboli}{4 servings}{90 minutes prep, 30 minutes cooking}

\Ingredient{\fr72 cups bread flour}
\Ingredient{1 teaspoon sugar}
\Ingredient{\fr94 teaspoons yeast}
\Ingredient{2 teaspoons salt}
\Ingredient{\fr32 cups warm water}
\Ingredient{2 tablespoons olive oil, plus 2 teaspoons}
Mix everything but water together with a wooden spoon, then slowly add in water until your dough combines. Knead for about 6 minutes and put it in a bowl drizzled with olive oil to rise (1 hour if warm and draft free.)\\


After it has risen, get a piece of parchment the size of your pan and cut dough ball in half. Stretch the half to make a rectangle shape (should fit pretty perfectly in a standard sheet pan) and make sure it isn't too thick in the middle.

\Ingredient{\fr14 cup pizza sauce of your choice}
\Ingredient{\fr12 cup cheddar, shredded}
\Ingredient{\fr14 cup parmesan, shredded}
\Ingredient{\fr34 cup mozzarella, shredded}
\Ingredient{A good amount of salami or pepperoni slices}
Preheat oven to 500 degrees with a sheet pan or pizza stone inside while it preheats.
Spread sauce all over, leaving an inch border dry. Sprinkle Cheddar, Parmesan, mozzarella cheese, and make three rows of salami or pepperoni (any meat will do) Sprinkle a little more cheese on top of that.

\Ingredient{1 egg}
\Ingredient{1 tablespoon water}
\Ingredient{1 teaspoon oregano}
\Ingredient{1 teaspoon thyme}
\Ingredient{\fr12 teaspoon garlic powder}
Brush edges of dough with a little egg wash (single egg mixed with tablespoon of water) and roll dough lengthwise into a log, seam side down.
Egg wash the log, sprinkle with herbs, %or Italian seasoning,
Parmesan, garlic powder, and cut 5 diagonal slits across the log to allow steam to release.
Remove hot sheet pan from oven, place Stromboli on parchment onto pan and put in the oven. Drop temperature to 400 immediately and cook for about 30 minutes. Top should be golden and bubbly.
You can refrigerate the other dough half for pizza later in the week, and you can really use any filling you want.

\end{recipe}

\end{document}
