\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Thanksgiving Dinner}{Lots}{5-6 hours}

\Ingredient{turkey}
\Ingredient{1 tablespoon salt}
Rinse turkey and rub the insides with salt. Let sit for a while.

\Ingredient{\fr14 cup onion}
\Ingredient{\fr14 cup celery}
\Ingredient{1 teaspoon sage}
\Ingredient{\fr14 teaspoon thyme}
\Ingredient{1 bay leaf}
\Ingredient{several peppercorns}
\Ingredient{several allspice berries}
While it is sitting, set the neck, heart and gizzard cooking with celery and onion to make stock.

Prepare stuffing (see page \pageref{Stuffing}).

\Ingredient{1 tablespoon flour}
Put some stuffing in the turkey's neck cavity, then pin the cavity closed. Put turkey in the prepped browning bag. set to bake at 350\0F for however long it takes.
% I can't find the function right now, but it was on the order of m^0.8
\\

\Ingredient{2 tablespoons melted butter}
Mix the butter with the remaining stuffing. Bake it later, with the squash custard.

% \Ingredient{potatoes-1 medium per person}
% Peel and dice the potatoes.\\
% Pressure cooker operation:\\
% No salt in water. Cover the potatoes barely with water.\\
% Pull out red lock on the lid and put sealing ring in. Secure the lid.\\
% Set stove on medium high with the valve set on I. When it reaches pressure (the red thing pops up), cook for 4 minutes then turn the stove off. Once the red thing pops back down, open the valve and wait for the rest of the steam to discharge.
%
% \Ingredient{1 tablespoon per person butter}
% \Ingredient{\fr14 cup milk per person}
% \Ingredient{\fr18 teaspoon white pepper}
% Melt butter in milk. Mash the potatoes to small bits, then add milk and butter.\\
% The order is important. It's really hard to get the rest mashed after you add the milk.

\newstep
Make mashed potatoes as found on page \pageref{MashedPotatoes}.


\Ingredient{1 pomegranate}
\Ingredient{3 kiwis}
\Ingredient{4 clementines or 2 persimmons}
Pop the pomegranate. skin and dice the kiwi and clementine. Mix together. You can adjust the amounts of each for greatest aesthetic appeal.

\Ingredient{1 pound cranberries}
\Ingredient{1 cup water}
\Ingredient{1-2 cup sugar}
\Ingredient{\fr18 teaspoon salt}
Bring the cranberries and water to a boil with a lid on; they tend to pop. Once it starts boiling, add salt and sugar and turn down to a simmer until thick. This lasts for a while, so you can make it far in advance.

\Ingredient{5 ounces cream of mushroom soup}
\Ingredient{\fr34 cup milk}
\Ingredient{\fr18 teaspoon black pepper}
Mix in a \fr32 quart baking dish.

\Ingredient{\fr43 cup fried onions}
\Ingredient{4 cups cooked cut green beans}
Stir in beans and \fr23 cup onions. Bake at 350\0F for 30 minutes or until fully hot. Stir.\\
Top with the remaining onions. Bake 5 minutes or until the onions are golden.

% green beans
% whipping cream
% nutmeg
% Good green beans

\Ingredient{1 winter squash of choice - kuri or buttercup/kabocha}
\Ingredient{1 egg per cup of squash}
\Ingredient{1 tablespoon butter per cup of squash}
\Ingredient{1 tablespoon brown sugar per cup of squash}
\Ingredient{\fr14-\fr34 cup milk per cup of squash}
\Ingredient{\fr18 teaspoon salt}
\Ingredient{\fr12 teaspoon cinnamon}
\Ingredient{\fr18 teaspoon cloves}
\Ingredient{\fr14 teaspoon allspice}
\Ingredient{\fr14 teaspoon nutmeg}
In advance, bake the squash skin-side down with some water until tender.
Scrape out flesh. Mash/food-process the flesh. Whisk egg and preliminary amount of milk. Mix in with the squash, blending well.

\Ingredient{2 tablespoons cornstarch}
\Ingredient{2 tablespoons water}
When the turkey comes out of the oven, strain the stock and the turkey browning bag and put the liquids in a saucepan. This will become the gravy. Mix together the cornstarch and water until you get a thick liquid. Add slowly to the gravy base.

\end{recipe}

\end{document}
