\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[Pesto]{Basil Pesto}{24 ounces/2 dishes}{30 minutes}

\Ingredient{2 cups fresh basil leaves (see note)}
\Ingredient{\fr12 cup olive oil}
\Ingredient{2 tablespoons pine nuts}
\Ingredient{2 cloves garlic, peeled}
\Ingredient{1 teaspoon salt}
Put the basil, olive oil, pine nuts, garlic cloves and salt in the blender and mix at high speed.
Stop from time to time and scrape the ingredients down toward the bottom of the blender cup with a rubber spatula.\\
NOTE: The quantity of basil in most recipes is given in terms of whole leaves.
American basil, however, varies greatly in leaf sizes.
There are small, medium, and very large leaves, and they all pack differently in the measuring cup.
For the sake of accurate measurement, I suggest that you tear all but the tiniest leaves into two or more small pieces.
Be gentle, so as not to crush the basil.  This would discolor it and waste the first, fresh droplets of juice.

\newstep
At this point, you may want to divide the recipe. Half the recipe is good for a dish made for 4 people. Whatever remains can easily be frozen and used later.

%\Ingredient{\fr12 cup freshly grated Parmesan cheese}
%\Ingredient{2 tablespoons Romano pecorino cheese}
%\Ingredient{3 tablespoons butter, soft (optional, often not needed with the other oils)}
%When the ingredients are evenly blended, pour into a bowl and beat in the two grated cheeses by hand.
%When the cheese has been evenly incorporated into the other ingredients, beat in the softened butter.
%Before spooning the pesto over pasta, add to it a tablespoon or so of the hot water in which the pasta has boiled.

\end{recipe}

\end{document}
