\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Browned Butter Chocolate Chip Cookies}{20 cookies}{20 minutes prep + 2 hours chilling + 10 minutes baking}

\Ingredient{\flour{\ap}{9}{4}}
\Ingredient{1 teaspoon baking soda}
\Ingredient{\fr14 teaspoon sea (or table) salt}
Whisk together in a bowl and set aside.

\Ingredient{1 cup unsalted butter (unsalted makes a difference here)}
Melt butter in a saucepan over medium heat. The butter will start to foam. Make sure you whisk consistently during this process. After a couple of minutes, the butter will begin to brown on the bottom of the saucepan. Continue to whisk and remove from heat as soon as the butter begins to brown and give off a nutty aroma. Immediately transfer the butter to a large bowl to prevent burning. Set aside to cool for a few minutes.

\Ingredient{\fr32 cup dark brown sugar}
\Ingredient{\fr14 cup white sugar}
Mix together the sugar and butter.

\Ingredient{1 egg and an extra yolk}
\Ingredient{2 teaspoons vanilla extract}
\Ingredient{1 tablespoon greek yogurt (whole milk or heavy cream might actually be better)}
\Ingredient{\fr32 cup semi-sweet chocolate chips}
Beat in the egg, vanilla, and yogurt until combined. Add the dry ingredients until just combined. Mix in the chocolate chips. Put in the fridge to chill for 2 hours.

\Ingredient{Some sea salt (optional)}
Preheat the oven to \tempf{350}.\\
Make balls of about \fr14 cup of dough. Sprinkle with a little sea salt.
Bake the cookies 9-11 minutes or until the edges are golden brown. Let the cookies start cooling while still on the sheet, and transfer them to a cooling rack after a few minutes to finish cooling.


\end{recipe}

\end{document}
