\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Chicken Breasts With Steam-Roasted Parsnips, Leeks, and Thyme}{4 servings}{30 minutes}
	% From january 2011 Sunflower Market magazine

\Ingredient{1 medium leek}
Cut lengthwise then thinly slice white part crosswise.

\Ingredient{1 pound parsnips}
\Ingredient{2 teaspoons fresh thyme leaves}
Place with the leek in a dish with \fr14 cup water and microwave until easily pierced with a fork, about 5 minutes. Drain water and set aside.

\Ingredient{4 skin-on chicken breasts}
Preheat oven to \tempf{400}. Flatten chicken to \fr12 inch to facilitate chicken.

\Ingredient{1 sprig rosemary, leaves removed and chopped}
\Ingredient{\fr14 teaspoon salt}
\Ingredient{\fr14 teaspoon black pepper}
\Ingredient{1 tablespoon \ww}
Mix together and dredge chicken in the mixture.

\Ingredient{3 tablespoons olive oil}
Toss vegetables in half of the oil, season with salt and pepper, and place in top third of oven to roast for 15 minutes.
Coat a 12-inch skillet with the remaining oil and place over medium-high heat. When oil is hot, place chicken in pan, skin down, and brown for 2-3 minutes. Do not move them; they'll stick at first but release easily once browned. Turn and brown other side for another 2-3 minutes. Transfer to a serving platter and keep warm.

\Ingredient{2 shallots, finely chopped}
\Ingredient{1 clove garlic, crushed}
Reduce stove to medium-low and saut\'e for 1-2 minutes.

\Ingredient{\fr14 cup white wine or water}
Deglaze pan with liquid and scrape everything up into a sauce.

\Ingredient{2 tablespoons chopped fresh italian parsley}
\Ingredient{2 tablespoons soy sauce}
Whisk in when the sauce's volume reduces by half. Place leek and parsnips around chicken and top with sauce.

\end{recipe}

\end{document}
