\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Chocolate Peanut Butter Tartlets}{20 servings}{1 hour}
% from december 2014 delicious living magazine

\Ingredient{\fr34 cup plus 2 tablespoons \ww}
\Ingredient{\fr14 cup cocoa powder}
\Ingredient{\fr14 cup sugar}
\Ingredient{\fr18 teaspoon salt}
Mix in a medium bowl.

\Ingredient{3 tablespoons butter, melted and cooled}
\Ingredient{3 tablespoons canola oil}
\Ingredient{\fr12 egg, beaten}
\Ingredient{\fr12 teaspoon vanilla extract}
Mix in a different bowl. Mix into the dry ingredients. Chill 15 minutes.

Grease mini muffin cups. Form dough into walnut-sized balls and place one in each cup. Gently push dough along bottom and sides of cup and chill another 15 minutes.

Preheat oven to 375\0F. Bake crusts 12-15 minutes. Cool completely before removing.

\Ingredient{\fr12 cup plus 2 tablespoons nonhydrogenated peanut butter}
\Ingredient{2 ounces cream cheese}
Cream together.

\Ingredient{\fr14 cup powdered sugar}
\Ingredient{\fr12 teaspoon vanilla extract}
Mix into the peanut butter.

\Ingredient{\fr14 cup plus 2 tablespoons heavy cream}
Whip to soft peaks and fold \fr14 into the butter mixture. Gradually fold in the rest.

\Ingredient{2 ounces dark chocolate (65\%)}
Melt slowly in microwave, stirring frequently.

\Ingredient{1 teaspoon canola oil}
Stir into the chocolate.

\Ingredient{\fr14 cup finely chopped peanuts (optional)}
Spoon peanut butter into crusts and smooth tops. Spoon chocolate over top. Sprinkle with peanuts and serve.
You can also refrigerate for a firmer texture and remove from refrigerator 5-10 minutes before serving.

\end{recipe}

\end{document}
