\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[CinnamonStar]{Cinnamon Star}{12 servings}{2.5 hours}
% https://www.kingarthurbaking.com/recipes/cinnamon-star-bread-recipe

\Ingredient{\flour{\ap}{5/3}}
\Ingredient{\fr14 cup (46 g) potato flour}
\Ingredient{\fr14 cup (28 g) dry milk}
Sift together thoroughly to prevent lumps.

\Ingredient{198--227 g lukewarm water}
\Ingredient{4 tablespoons (57 g) unsalted butter, room temperature}
\Ingredient{1 teaspoon vanilla extract}
\Ingredient{2 teaspoons instant yeast}
\Ingredient{2 tablespoons (25 g) sugar}
\Ingredient{1 teaspoon (6 g) salt}
Combine and knead to make a soft, smooth dough.
Place in a lightly greased bowl, cover, and let rise for 60 minutes until doubled in bulk.

Divide the dough into four equal pieces.
Shape each into a ball and allow to rest for 15 minutes.

\Ingredient{1 egg, beaten}
\Ingredient{\fr12 cup sugar}
\Ingredient{1 tablespoon cinnamon}
Roll one of the dough pieces into a 10" circle.
Place onto a piece of parchment paper.
Brush a thin coat of egg over the surface, then sprinkle with \fr13 of the cinnamon sugar, leaving \fr14" of bare dough around the circumference.
Repeat for the other three pieces, layering them on each other, leaving the top of the stack bare.
Place a 3" round cutter in the center of the circle as a guide.
Cut the circle into 16 pieces from the guide to the edge, all the way through the layers.
Pick up two adjacent strips and twist them away from each other twice.
Repeat until you have 8 pairs of strips.
Pinch the pairs of strips together to create star-like points.
Transfer the parchment with the star to a baking sheet.
Cover the star and let rise for 45 minutes, until it becomes noticeably puffy.

\preheat{400}
Brush the whole star with a thin coat of the beaten egg.
Bake for 12 to 15 minutes until it's golden brown.

\end{recipe}

\end{document}

