\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Fresh Blueberry Tart}{12 servings}{1 hour}
% from unknown delicious living magazine

\Ingredient{\flour{all-purpose}{3/4}}
\Ingredient{\flour{whole wheat}{1/4}}
\Ingredient{2 tablespoons sugar}
\Ingredient{\fr12 teaspoon salt}
\Ingredient{1 stick cold butter, chopped}
Mix until butter is broken into pea-sized pieces.

\Ingredient{3 tablespoons almond butter}
Add and mix about 1 minute more. Rub any remaining large pieces with flour to break them up.

\Ingredient{1 egg yolk}
\Ingredient{2 tablespoons cold water}
Add egg and enough water to hold the dough together. Roll the dough into a disk. Optionally refrigerate.
Transfer the dough to a 9-inch tart pan with removable sides. Make sure sides are about \fr14-inch thick.

Preheat oven to \tempf{375} and place a baking tray in the lower third of the oven.
Line tart pan with foil, fill with beans or pie weights, set on tray, and bake until foil peels away easily, about 15 minutes. Carefully remove foil and filler. Return empty tart shell to oven on middle rack. Bake until golden brown all over, about 10--15 minutes. Let cool.

\Ingredient{1 pint fresh blueberries}
\Ingredient{1 tablespoon maple syrup}
\Ingredient{1 teaspoon fresh lime juice}
Just before serving, combine in a small saucepan and heat until juices release, about 5 minutes.

\Ingredient{8 ounces thick honey yogurt}
Spread yogurt into cooled tart shell and fill with blueberries.

\end{recipe}

\end{document}
