\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[HoneyRolls]{Honey Rolls}{12 rolls}{3 hours}
    % https://www.reddit.com/r/Breadit/comments/swals9/pictures_do_not_do_them_justice_these_are_hands/hxl5oj1/
    % https://cookingformysoul.com/super-soft-honey-dinner-rolls/
\Ingredient{\milk{1}, warmed}
\Ingredient{\yeast{9/4}}
\Ingredient{1 teaspoon sugar}
Combine in a stand mixer bowl.
Stir then let stand for about 10 minutes until frothy.

\Ingredient{2 eggs}
\Ingredient{\fr14 cup unsalted butter, melted but cooled}
\Ingredient{1 teaspoon kosher salt}
\Ingredient{\honey{1/3}}
With the dough hook on low speed, mix these together.

\Ingredient{\flour{bread}{7/2}}
Increase speed to medium and add flour 1 cup at a time, until you reach 3 cups.
Continue adding flour by \fr14 cup increments until the dough is slightly sticky.
Transfer to a floured surface and knead for about 4 minutes.
The dough should be moist, slightly sticky, and spring slowly when poked.
Don't overknead as it will toughen the bread.

Form into a ball and place in a lightly oiled bowl, turning to coat the dough.
Cover and let rise in a warm environment for about 1 hour, until doubled in size.

Punch down the dough and transfer to a clean surface.
Cut into 12 equal pieces, shape into rolls, and arrange in a greased 9\X13 baking pan.
Cover again and let rise for another hour until doubled in size.

\preheat{350}{beginning} while rising.
Brush with melted butter.
Bake for 15-20 minutes.
Let cool slightly.

\Ingredient{\fr12 cup unsalted butter, softened}
\Ingredient{\honey{1/4}}
Whisk together and use as a spread or topping.
\end{recipe}

\end{document}
