\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[HoneyWheatRolls]{Honey Wheat Rolls}{24 rolls}{40 minutes prep, long rise}
% https://www.kingarthurbaking.com/recipes/honey-wheat-rolls-recipe
	\Ingredient{\yeast{9}{4}}
	\Ingredient{\milk{1}, lukewarm}
	\Ingredient{pinch sugar}
	Dissolve the yeast in 2 tablespoons of the milk with the sugar. Let sit until it bubbles, about 15 minutes.
	Combine with the rest of the milk.

	\Ingredient{\fr14 cup (57 g) orange juice\footnotemark}
	\Ingredient{4 tablespoons (57 g) softened unsalted butter, in chunks}
	\Ingredient{3 tablespoons (64 g) honey}
	\Ingredient{\flour{all-purpose}{4/5}}
	\Ingredient{\flour{whole wheat}{3/2}}
	\Ingredient{\fr54 teaspoon (8 g) salt}
	\Ingredient{\fr14 cup (43 g) potato flour}
	Mix all ingredients together to make a smooth dough.
	Place in a lightly greased bowl.
	Cover and let rise until not quite doubled.
	While rising, grease a 9"\X13" pan.

	Divide into 24 pieces (about 33 g each).
	Form into rolls. Place in the pan and cover with plastic wrap. Allow the rolls to rise for 1 \fr12--2 hours. They'll expand into each other.
	While the rolls are rising, preheat the oven to \tempf{350}.

	Bake the rolls for 15 minutes then, if they're browning too quickly, tent them with aluminum foil.
	Continue to bake until they're mahogany-brown on top but lighter on the sides, an additional 10--13 minutes.
\end{recipe}
\footnotetext{Doesn't add its own flavor, just negates any bitterness from the whole wheat}
\end{document}

