\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Mongolian Beef}{2 servings}{1.5 hours prep/marinading}

\Ingredient{8 ounces flank steak, sliced into \fr14 inch thick strips}
\Ingredient{1 teaspoon oil}
\Ingredient{1 teaspoon soy sauce}
\Ingredient{1 tablespoon cornstarch}
Marinate the beef in oil, soy sauce, and cornstarch mixture for an hour.

\Ingredient{\fr18 cup cornstarch} %was this cut in half?
Dredge the meat in the cornstarch until lightly coated.

\Ingredient{enough vegetable oil to make a 1-centimeter layer in the bottom of your pan}
Heat the oil on high heat. Just before it hits smoke point, or when it starts to evaporate, put the steak pieces in the pan and fry for 1 minute on one side and 30 seconds on the other. Do this in batches that can comfortably fit in the pan.
Remove each piece as it is finished and place on a sheet pan to the side. If the meat is letting out oil, prop up one side of the pan to drain the oil away from the meat.

\Ingredient{\fr12 teaspoon minced or crushed fresh ginger}
\Ingredient{5 dried red chili peppers or \fr52 teaspoons chili flakes}
Drain most of the oil, leaving about 2 millimeters behind. Turn the heat down to medium.
Add the ginger and chili to the mixture. Stir for about 15 seconds.

\Ingredient{4 cloves garlic, minced or crushed}
Then add the garlic and stir for another 10 seconds.

\Ingredient{\fr14 cup soy sauce}
\Ingredient{\fr14 cup water}
Add the liquids. Bring the sauce to a simmer.

\Ingredient{2 tablespoons brown sugar}
Add the sugar and stir until completely dissolved. Let the sauce simmer for another couple minutes.

\Ingredient{1 tablespoon cornstarch, mixed with 1 tablespoon water}
Stir in the cornstarch mixture to thicken the sauce, and continue simmering until the sauce is adequately thick.

\Ingredient{2 scallions, sliced}
Add the beef and the scallions to the sauce and toss everything together, ensuring an even coat of sauce over everything.

\end{recipe}

\end{document}
