\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[OatmealWalnutBread]{Oatmeal Walnut Bread}{32 rolls or 2 loaves}{2 hours}
    \Ingredient{\flour{\ap}{2}}
    \Ingredient{5 teaspoons yeast}
    \Ingredient{2 teaspoons salt}
    Mix in a large bowl.

    \Ingredient{\fr32 cup water}
    \Ingredient{\fr13 cup molasses}
    \Ingredient{4 teaspoons shortening}
    Heat in a saucepan until very warm, about 120\0F. The shortening does not need to melt.
    Add to flour mixture. Blend at low speed until moistened, then beat for another 3 minutes at medium speed.

    \Ingredient{\fr23 cup rolled oats}
    \Ingredient{\flour{\ww}{4/3}}
    \Ingredient{1 cup walnuts, chopped}
    Stir in by hand to make a firm dough.
    Knead on a floured surface 5 to 8 minutes, resulting in a slightly sticky dough.
    Place in greased bowl, turning to grease the top as well.
    Cover. Let rise in a warm place about 30 minutes. Punch down.
    Divide into two parts. Shape each part into a round loaf or pan rolls.
    Place loaves on a greased cookie sheet or rolls into an 8" square, greased pan.
    Cover and let rise again for 40 minutes.

    \Ingredient{1 egg, beaten}
    \Ingredient{1 tablespoon water}
    \preheat{400}
    Beat together to make an egg wash. Brush the top of the bread.

    \Ingredient{2 tablespoons rolled oats}
    Sprinkle over the top of the bread.

    Bake at 400\0F for 20 to 25 minutes. Remove from pan quickly and cool.
\end{recipe}

\end{document}

