\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Oven-fried Chicken with Yogurt Dipping Sauce}{2 servings}{15 minutes prep, 15 minutes cooking}

\preheat{425}

\Ingredient{30 milliliters lemon juice}
\Ingredient{1 small garlic clove, crushed or chopped}
In a small bowl, add lemon juice and garlic. Let sit for 5 minutes.

\Ingredient{425 grams (\fr32 cup) Greek yogurt or sour cream}
\Ingredient{5 grams (2 tablespoons) chives, finely chopped}
\Ingredient{5 grams (2 tablespoons) parsley, finely chopped}
\Ingredient{5 grams (2 tablespoons) basil, finely chopped}
\Ingredient{Coarse salt and pepper to taste}
Mix in the yogurt and herbs.

\Ingredient{30 grams (2 tablespoons) unsalted butter}
\Ingredient{125 grams (\fr32 cup) panko bread crumbs}
On medium-high heat, melt the butter in an 8-inch skillet. When butter stops foaming, add bread crumbs and add pinches of salt and pepper. Cook, stirring often, until crumbs are a deep golden brown, 3 to 4 minutes. Add crumbs to a shallow baking dish and set aside.

\Ingredient{650 grams (\fr32 pound) chicken tenders or chicken breasts sliced into strips}
\Ingredient{Coarse salt and pepper to taste}
\Ingredient{2 large garlic cloves, minced}
\Ingredient{1 teaspoon lemon zest}
\Ingredient{25 grams (2 tablespoons) mayonnaise}
\Ingredient{15 grams (1 tablespoon) dijon mustard}
Dry the chicken well and season with salt and pepper. In a large bowl, mix together garlic, lemon zest, mayonnaise and mustard. Add chicken and mix well to coat each piece.\\
Lightly spray an oven-safe wire rack with oil spray and place it over a rimmed baking sheet. Dip chicken pieces into bread crumb mixture, pressing to adhere as many bread crumbs as possible. Shake off any excess and place breaded chicken on the wire rack. Bake until cooked through and golden brown, 12--15 minutes. Serve with herb yogurt dip.


\end{recipe}

\end{document}
