\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}{Raspberry Cheesecake Squares}{16 servings}{30 minutes prep, 55 minutes cooking}
% from June 2012 Sunflower Market magazine

Position one oven rack in middle and one in bottom of oven. Preheat oven to 350\0F. Line an 8\X8 glass baking dish with two perpendicular pieces of foil, leaving overhang.

\Ingredient{5 graham cracker sheets}
\Ingredient{\fr23 cup slivered almonds}
Finely grind together.

\Ingredient{2 tablespoons unsalted butter}
Add and process until mixture forms moist crumbs. Press into bottom of baking dish and chill.

\Ingredient{14 ounces cream cheese}
\Ingredient{\fr14 cup honey}
\Ingredient{\fr14 cup sugar}
Thoroughly beat together until smooth and creamy.

\Ingredient{1 cup nonfat greek yogurt}
Beat in.

\Ingredient{2 eggs}
\Ingredient{3 egg whites}
Beat in one at a time, until well blended each time. Pour batter over crust.

Place an oven-proof bowl of warm water on lower oven rack. Place cheesecake on middle rack and bake until set in center, about 45-55 minutes. Be careful not to brown the top.
When done, the cheesecake will still jiggle in the center but will set as it cools.
Remove from oven and let cool completely. Remove from pan using foil and cut apart.

\Ingredient{2 tablespoons seedless raspberry preserves}
Heat in a very small saucepan (or in the microwave) with 1 tablespoon water until melted and a bit bubbly.

\Ingredient{2 cups raspberries}
Arrange raspberries with the sauce on top of the cheesecake and serve.

\end{recipe}

\end{document}
