\documentclass[../Cookbook.tex]{subfiles}

\pagenumbering{arabic}
\begin{document}

\begin{recipe}{Thanksgiving Dinner}{Lots}{5--6 hours}

To do in advance: \\
Cranberry sauce, as on \reciperef{CranberrySauce}.

Baking the squash for squash custard (\reciperef{SquashCustard}).

\newstep
On the day of: \\
Fruit salad, as on \reciperef{FruitSalad}.

\Ingredient{turkey}
\Ingredient{1 tablespoon salt}
Rinse turkey and rub the insides with salt. Let sit for a while.

\Ingredient{\fr14 cup onion}
\Ingredient{\fr14 cup celery}
\Ingredient{1 teaspoon sage}
\Ingredient{\fr14 teaspoon thyme}
\Ingredient{1 bay leaf}
\Ingredient{several peppercorns}
\Ingredient{several allspice berries}
While it is sitting, set the neck, heart and gizzard cooking with celery and onion to make stock.

Prepare stuffing (see \reciperef{Stuffing}).

\Ingredient{1 tablespoon flour}
\begin{minipage}{.7\textwidth}
	Put some stuffing in the turkey's neck cavity, then pin the cavity closed.
	Prepare the browning bag by shaking the flour around in it to coat the inside.
	Put turkey in the prepped browning bag.
	Set to bake at \tempf{325} for a number of hours given by this function:
	$ t = \frac{W^{\nicefrac{2}{3}}}{1.5} $
	where weight is in pounds.
	If you don't feel like calculating precisely, consult the table.
\end{minipage}
\begin{minipage}{.29\textwidth}
	\begin{tabular}{cl}
		Weight & Cook time \\ \hline
		15 lb & 4h 3min \\
		17 lb & 4h 24min \\
		18 lb & 4h 35min \\
		19 lb & 4h 45min \\
		20 lb & 4h 55min \\
		21 lb & 5h 4min \\
		23 lb & 5h 24min
	\end{tabular}
\end{minipage}

\Ingredient{2 tablespoons melted butter}
Mix the butter with the remaining stuffing. Bake it later, with the squash custard.

\newstep
Make rolls as on \reciperef{DinnerRolls}.

\Ingredient{5 ounces cream of mushroom soup}
\Ingredient{\milk{3}{4}}
\Ingredient{\fr18 teaspoon black pepper}
Mix in a \fr32 quart baking dish.

\Ingredient{\fr43 cup fried onions}
\Ingredient{4 cups cooked cut green beans}
Stir in beans and \fr23 cup onions. Bake at \tempf{350} for 30 minutes or until fully hot. Stir.\\
Top with the remaining onions. Bake 5 minutes or until the onions are golden.

\newstep
Make the custard part of the squash custard (\reciperef{SquashCustard}).

\newstep
Make green beans as on \reciperef{CreamBeans}.
Make mashed potatoes as found on \reciperef{MashedPotatoes}.

\Ingredient{2 tablespoons cornstarch}
\Ingredient{2 tablespoons water}
When the turkey comes out of the oven, strain the stock and the turkey browning bag and put the liquids in a saucepan. This will become the gravy. Mix together the cornstarch and water until you get a thick liquid. Add slowly to the gravy base.

\end{recipe}

\end{document}
