\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[VegetarianChili]{\textbf{Vegetarian Chili}}{6 servings}{50 minutes}
%	https://www.wellplated.com/instant-pot-vegetarian-chili/

\Ingredient{1 tablespoon olive oil}
\Ingredient{1 medium yellow onion, diced}
To a 6-quart or large Instant Pot, add the olive oil. Turn to SAUTE and let the oil heat. Once the oil is hot, add the onion and cook until beginning to soften, about 3 minutes.

\Ingredient{2 medium sweet potatoes, chopped}
\Ingredient{2 medium red bell peppers, chopped}
\Ingredient{4 cloves garlic, minced}
\Ingredient{1 tablespoon chili powder}
\Ingredient{1 teaspoon ground cumin}
\Ingredient{1 teaspoon chipotle chili powder}
\Ingredient{\fr54 teaspoons kosher salt}
Add the sweet potatoes, bell pepper, garlic, chili powder, chipotle chili powder, cumin, and kosher salt. Cook for 1 to 2 additional minutes, until the garlic is fragrant.

\Ingredient{\fr52 cup vegetable broth}
Add half of the vegetable broth and stir, scraping up any stuck-on bits of food (this will prevent a burn warning).

\Ingredient{1 8-ounce can tomato sauce}
\Ingredient{\fr12 cup quinoa}
Stir in the remaining broth and the quinoa. Pour the tomato sauce on top (do not stir again).
Cover and seal the Instant Pot. Cook on manual (HIGH) pressure for 8 minutes. Immediately release the pressure. Carefully open the Instant Pot.

\Ingredient{1 (15-ounce) can black beans, rinsed}
\Ingredient{1 (15-ounce) can kidney beans, rinsed}
\Ingredient{\fr12 teaspoon granulated sugar}
Turn the Instant Pot to OFF. Stir in the black beans, kidney beans, and sugar. Place the lid back on top and let stand 10 minutes to thicken. Uncover. Taste and adjust seasoning as desired. Serve hot, with any and all the toppings!

\end{recipe}

\end{document}
