\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[WhiteBread]{White Bread}{1 loaf}{45 minutes prep + 1.5 hours rising + 40 minutes baking}
% https://www.notion.so/White-Bread-c78f276ded104fa59b1c42cc242415d0
\Ingredient{230g whole milk, lukewarm}
\Ingredient{75g water, lukewarm}
\Ingredient{42g honey}
\Ingredient{9g yeast}
Combine in the bowl of a stand mixer. Let rest 15 minutes or until foamy.

\Ingredient{\fr32 teaspoon salt}
\Ingredient{400g \ap flour}
Add to the liquid mixture and knead briefly.

\Ingredient{30g unsalted butter, room temperature}
When most of the flour is absorbed, add in the butter.
At this point, the dough should not be sticking to the sides of the bowl at all.
If it is, slowly add in more flour, up to \fr14 cup until it starts to pull away from the sides of the bowl.
If the dough seems dry/dense, add up to 2 tablespoons water until it starts to become more slack.
Continue to knead for 6-10 minutes, until the dough is smooth.

Grease a bowl and a loaf pan with unsalted butter.
Remove dough from the mixer and form it into a ball with your hands.
Plop the dough ball into the greased bowl and cover with cotton or paper towel.
Put the dough in a warm place for 45 minutes, until more than doubled.

Grease a surface with some unsalted butter.
Punch down the dough and turn it out onto the greased area.
Flatten it into a rectangle with the shorter side being the length of your loaf pan.
Roll the dough tightly, keeping the short axis constant.
Plop the roll into the pan with the seal side down.
Cover the loaf with the towel from earlier and let rise another 45 mintues.

Preheat oven to 350 with a metal pan in it.
Boil 3 cups of water.
After the loaf has risen, it should have filled out the pan almost to the rim.
If you gently poke it, it should begin to spring back but remain dented.
If necessary, it can go another 15 minutes.
Score the loaf down the center of its long axis about half an inch deep.
Put your loaf in the preheated oven, and dump the boiling water in the preheated pan.
Bake for 35-40 minutes.
The loaf will be dark tan with an internal temperature of \tempf{190}.
Immediately remove loaf from pan and allow to cool at least 30 minutes before slicing.

\end{recipe}

\end{document}

