\documentclass[../Cookbook.tex]{subfiles}

\begin{document}

\begin{recipe}[PizzaDough]{Whole Wheat Pizza Dough}{2 dough balls}{30 minutes prep, 1.5 hours rising, 15 minutes post-prep}

\Ingredient{\flour{all-purpose}{9/4}}
\Ingredient{\flour{whole wheat}{4/3}}
\Ingredient{\yeast{5/2}}
\Ingredient{2 teaspoon salt}
\Ingredient{1 teaspoon sugar}
Combine in a food processor. Pulse to mix.

\Ingredient{\fr54 cup warm (\tempf{110}) water plus some extra as needed}
\Ingredient{2 tablespoon olive oil, plus more as needed}
Run continuously while adding water and olive oil in a steady stream, then pulse until the dough comes roughly together, about 12 seconds. If the dough does not form into a ball, sprinkle with 1--2 teaspoons water and pulse again.

\newstep
Let the dough rest for 5--10 minutes. Process again for 25--30 seconds, steadying the food processor. The dough should be tacky but not sticky. Transfer to a lightly floured work surface and form into a smooth ball.
Place in a large oiled bowl, turn to coat with oil, and cover.
Let rise in a warm place until doubled in volume.

\newstep
Turn the dough out onto a lightly floured work surface, punch it down, and form into a smooth cylinder. Divide the dough into 2 equal pieces. Shape each into a smooth ball, dusting with flour only if the dough becomes sticky. Cover both balls with a clean towel and let rest for 10 minutes before rolling.



Can be frozen for up to 2 months in an airtight bag. Thaws in 3--4 hours.

\end{recipe}

\end{document}
